NGO analysis

### 2022-07-24 Shiny/Test/Dashboard downloads test.Rmd
Including link to Excel template.

Then upload an Excel file in the set format.

@@

  output$downloadUI <- renderUI( {
  downloadButton("report", "Generate report")
})

@@

      params <- list(htmlfile = input$html$datapath,
                     excelfile = input$excel$datapath,
                     start = input$start,
                     end = input$end)

      rmarkdown::render(tempReport, output_file = file,
                        params = params,
                        envir = new.env(parent = globalenv()))
    }
  )

>>>>

Then upload an Excel file in the set format (available [here](https://github.com/amaliehc/ISSSV1337/blob/5c0a8a2beae499b3d2524a3965ceebf3b3ebad0e/Dashboard/Data/NGO_template.xltx)).

@@

output$downloadUI <- renderUI({
  downloadButton("report", "Generate report")
})

@@

    params <- list(
      htmlfile = input$html$datapath,
      excelfile = input$excel$datapath,
      start = input$start,
      end = input$end
    )

    rmarkdown::render(tempReport,
      output_file = file,
      params = params,
      envir = new.env(parent = globalenv())
    )
  }
)
